% Progress Report Document
\documentclass[progress]{cmpreport}
\makeatletter
\input{t1pcr.fd}
\makeatother
\setlength{\footnotesep}{3ex}
\title{\Codex: A Website and Progressive Web App in Node.js \& React for table-top role-playing games}
\author{Christopher Alastair Irvine}
\registration{100036248}
\supervisor{Dr Katharina Huber}
\ccode{CMP-6013Y}
\summary{This document is the Progress Report for Codex}
\acknowledgements{
	I would like to thank Dr Katharina Huber for taking on the supervision of this project, 
	and guiding me towards greatness. Additionally I would like to thank Wizards of the Coast 
	for their generosity and kindness in allowing the use of their Intellectual Property for this project.
}
\usepackage{rotating}
\newcommand{\ueacmp}{UEA School of Computing Sciences}
\newcommand{\WotC}{Wizards of the Coast}
\newcommand{\dnd}{D\&D}
\newcommand{\sem}{Software Engineering Model}
\newcommand{\sems}{Software Engineering Models}
\newcommand{\Codex}{\textsc{Codex}}
\newcommand{\AgileSolo}{\emph{Agile Solo}}
% EOF Preamble and Macros
	
% BOF Document
\begin{document}
	% BOF Introduction
	\section{Introduction} \label{intro}
	% Introduction to the project: 
	% What is D&D?
	Dungeons and Dragons (\dnd) is a popular table-top role-playing game. Where a group of players (known as the Party), must find a way past a series of challenges (called the Campaign), created by the Dungeon Master (DM), as they explore the world that the DM has created. What happens during a Campaign is determined by a series of dice rolls that decide if an attack hits an enemy or if a lock is picked open. 
	% Problems with D&D
	In \dnd \ only the DM knows what is going to happen next, as a result a DM must be prepared for every eventuality that the Party might trigger. \WotC \, the company that created \dnd \ has a series of Campaigns that take the burden of preparing content away from the DM. But many DM's choose to create their own content or will stray from the content provided in the \WotC Campaigns. 
	% What is Codex? 
	% What is the purpose? 
	% What problems does Codex solve? 
	% How will it solve them?
	
	\section{\Codex \ Design}
	% Cherry pick sections from the Design Document, summarising how Codex is designed and why I made those choices. 
	
	\section{\Codex \ Implementation}
	% How will the design be implemented? SEM used? Trello? Languages? Technologies? MoSCoW
	
	\section{\Codex \ Progress}
	% Where are we at with Codex? Is it as far as we wanted to be? If not, why? How can be improve on the progress? What comes next?
	
	\section{Outstanding Issues}
	% What are the issues with Codex? Are they being addressed? Any forthcoming issues? 
		\subsection{Solutions}
		% How are the solutions with Codex being addressed? Mitigate potential future issues?
		
	\section{Conclusion}
	% Summarise the progress that I have made, if it is enough and if not how can we do more?
	
	\appendix
	\section{Gantt Chart - Original}
	\section{Gantt Chart - New}
	
\bibliography{projectbib}
\end{document}
% EOF Document